An Audio-Based 3D Spatial Guidance AR System for Blind Users

### 2020-06-01 manuscript.tex
Update structure: Overleaf first

% This is template.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04

\documentclass[runningheads]{res/templates/llncs}

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{etoolbox}

% Include packages from YAML header

@@

\title{An Audio-Based 3D Spatial Guidance AR System for Blind Users\thanks{Thank you for ...}}

\titlerunning{Audio-Based 3D Spatial Guidance}
%
\newbool{flag}
\boolfalse{flag}
%
\author{
\ifbool{flag}{\and}{\booltrue{flag}}James Coughlan\inst{1}\orcidID{0000-0003-2775-4083}
\ifbool{flag}{\and}{\booltrue{flag}}Brandon Biggs\inst{1}\orcidID{0000-1111-2222-3333}
\ifbool{flag}{\and}{\booltrue{flag}}Marc-Aurèle Rivière\inst{2}\orcidID{0000-0002-5108-3382}
\ifbool{flag}{\and}{\booltrue{flag}}Huiying Shen\inst{1}\orcidID{0000-1111-2222-3333}
}
%
\authorrunning{J. Coughlan et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\boolfalse{flag}
%
\institute{
\ifbool{flag}{\and}{\booltrue{flag}}
 The Smith-Kettlewell Eye Research Institute, San Francisco, CA \\
 \email{\href{mailto:coughlan@ski.org}{\nolinkurl{coughlan@ski.org}},
\href{mailto:brandon.biggs@ski.org}{\nolinkurl{brandon.biggs@ski.org}},
\href{mailto:hshen@ski.org}{\nolinkurl{hshen@ski.org}}} 
\ifbool{flag}{\and}{\booltrue{flag}}
 LITIS, University of Rouen, Normandy, France \\
 \email{\href{mailto:marc-aurele.riviere@univ-rouen.fr}{\nolinkurl{marc-aurele.riviere@univ-rouen.fr}}} 
}

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Augmented reality (AR) has great potential for blind users because it
enables a range of applications that provide audio information about
specific locations or directions in the user's environment. For
instance, the CamIO (``Camera Input-Output'') AR app makes physical
objects (such as documents, maps, devices and 3D models) accessible to
blind and visually impaired persons by providing real-time audio
feedback in response to the location on an object that the user is
touching (using an inexpensive stylus). An important feature needed by
blind users of AR apps such as CamIO is a 3D spatial guidance feature
that provides real-time audio feedback to help the user find a desired
location on an object. We have devised a simple audio interface to
provide verbal guidance towards a target of interest in 3D. The
experiment we report with blind participants using this guidance
interface demonstrates the feasibility of the approach and its benefit
for helping users find locations of interest.
\\
\boolfalse{flag}
\keywords{
\ifbool{flag}{\and}{\booltrue{flag}}
Assisitive Devices
\ifbool{flag}{\and}{\booltrue{flag}}
Augmented Reality
\ifbool{flag}{\and}{\booltrue{flag}}
Auditory Substitution
\ifbool{flag}{\and}{\booltrue{flag}}
Visual Impairment
}
\end{abstract}
%
%
\hypertarget{sota}{%
\section{State of the Art and Related Technology}\label{sota}}

@@

\begin{figure}
\includegraphics[width=0.55\linewidth]{res/img/fig1a} \includegraphics[width=0.45\linewidth]{res/img/fig1b} \caption{(left) Blind participant uses CamIO to explore a toy fire truck. The participant holds the CamIO stylus (a barcode pattern printed on a square wooden dowel with a pointy tip) to point to possible hotspots on the truck. The truck is glued to the board, a piece of paper with a separate barcode pattern, which is taped to the table. An iPhone 8 running CamIO is held by a gooseneck cellphone holder to capture a view of the truck, board and stylus. (right) Stylus points to steering wheel in the truck cabin. Though the steering wheel is in a recessed location that is not visible to CamIO, the stylus tip location can still be estimated.}\label{fig:exp}
\end{figure}

@@

Future work will focus on refining and improving the audio interface.
One possible way to speed up the guidance process is to add more
specific directional feedback, e.g., ``far left'' would tell the user to
move the stylus farther to the left than the ``left'' instruction. The
verbal directions could be augmented with 3D spatialized sound as in
\cite{mayAuditoryDisplaysFacilitate2019}, which could make the guidance
more intuitive. Finally, we will continue to test and improve the CamIO
system, with an emphasis on refining the spatial accuracy of the tip
location estimates using improved computer vision algorithms.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{res/templates/splncs04}
% \bibliography{bibliography}
\bibliography{res/refs.bib}

>>>>

\documentclass[runningheads]{res/templates/llncs}
%
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[hyphens]{url}
\usepackage{hyperref}

@@

\title{An Audio-Based 3D Spatial Guidance AR System for Blind Users\thanks{Thank you for ...}}
\titlerunning{Audio-Based 3D Spatial Guidance}

\author{James Coughlan\inst{1}\orcidID{0000-0003-2775-4083} \and
Brandon Biggs\inst{1} \and
Marc-Aurèle Rivière\inst{2}\orcidID{0000-0002-5108-3382} \and
Huiying Shen\inst{1}}

\authorrunning{J. Coughlan et al.}

\institute{The Smith-Kettlewell Eye Research Institute, San Francisco, CA \\
\email{\{coughlan, brandon.biggs, hshen\}@ski.org} \and
LITIS, University of Rouen, Normandy, France \\
\email{marc-aurele.riviere@univ-rouen.fr}}
%
\maketitle %
%
\begin{abstract}
Augmented reality (AR) has great potential for blind users because it
enables a range of applications that provide audio information about
specific locations or directions in the user's environment. For
instance, the CamIO (``Camera Input-Output'') AR app makes physical
objects (such as documents, maps, devices and 3D models) accessible to
blind and visually impaired persons by providing real-time audio
feedback in response to the location on an object that the user is
touching (using an inexpensive stylus). An important feature needed by
blind users of AR apps such as CamIO is a 3D spatial guidance feature
that provides real-time audio feedback to help the user find a desired
location on an object. We have devised a simple audio interface to
provide verbal guidance towards a target of interest in 3D. The
experiment we report with blind participants using this guidance
interface demonstrates the feasibility of the approach and its benefit
for helping users find locations of interest.

\keywords{Assisitive Devices
\and Augmented Reality
\and Auditory Substitution
\and Visual Impairment}
\end{abstract}
%

\hypertarget{sota}{%
\section{State of the Art and Related Technology}\label{sota}}

@@

\begin{figure}
\includegraphics[width=0.55\linewidth]{res/img/fig1a}
\includegraphics[width=0.45\linewidth]{res/img/fig1b} 
\caption{(left) Blind participant uses CamIO to explore a toy fire truck. The participant holds the CamIO stylus (a barcode pattern printed on a square wooden dowel with a pointy tip) to point to possible hotspots on the truck. The truck is glued to the board, a piece of paper with a separate barcode pattern, which is taped to the table. An iPhone 8 running CamIO is held by a gooseneck cellphone holder to capture a view of the truck, board and stylus. (right) Stylus points to steering wheel in the truck cabin. Though the steering wheel is in a recessed location that is not visible to CamIO, the stylus tip location can still be estimated.}
\label{fig:exp}
\end{figure}

@@

Future work will focus on refining and improving the audio interface.
One possible way to speed up the guidance process is to add more
specific directional feedback, e.g., ``far left'' would tell the user to
move the stylus farther to the left than the ``left'' instruction. The
verbal directions could be augmented with 3D spatialized sound as in
\cite{mayAuditoryDisplaysFacilitate2019}, which could make the guidance
more intuitive. Finally, we will continue to test and improve the CamIO
system, with an emphasis on refining the spatial accuracy of the tip
location estimates using improved computer vision algorithms.

% ---- Bibliography ----
\bibliographystyle{res/templates/splncs04}
\bibliography{res/refs.bib}

### 2020-06-01 res/manuscript.Rmd
Update structure: Overleaf first

---
title: "An Audio-Based 3D Spatial Guidance AR System for Blind Users"
titlerunning: Audio-Based 3D Spatial Guidance
authorrunning: J. Couhlan et al.
thanks: Merci !
output:
  pdf_document:
    template: res/templates/template.tex
    toc: no
    keep_tex: yes
  word_document:
    reference_docx: res/templates/template.docx
    toc: no
institutes:
- id: 1
  name: The Smith-Kettlewell Eye Research Institute, San Francisco, CA
  emails: coughlan@ski.org, brandon.biggs@ski.org, hshen@ski.org
- id: 2
  name: LITIS, University of Rouen, Normandy, France
  emails: marc-aurele.riviere@univ-rouen.fr
keywords:
- Assisitive Devices
- Augmented Reality
- Auditory Substitution
- Visual Impairment
abstract: Augmented reality (AR) has great potential for blind users because it enables
  a range of applications that provide audio information about specific locations
  or directions in the user’s environment. For instance, the CamIO (“Camera Input-Output”)
  AR app makes physical objects (such as documents, maps, devices and 3D models) accessible
  to blind and visually impaired persons by providing real-time audio feedback in
  response to the location on an object that the user is touching (using an inexpensive
  stylus). An important feature needed by blind users of AR apps such as CamIO is
  a 3D spatial guidance feature that provides real-time audio feedback to help the
  user find a desired location on an object. We have devised a simple audio interface
  to provide verbal guidance towards a target of interest in 3D. The experiment we
  report with blind participants using this guidance interface demonstrates the feasibility
  of the approach and its benefit for helping users find locations of interest.
authors:
- name: James Coughlan
  orcid: 0000-1111-2222-3333
  inst: 1
- name: Brandon Biggs
  orcid: 0000-1111-2222-3333
  inst: 1
- name: Marc-Aurèle Rivière
  orcid: 0000-0002-5108-3382
  inst: 2
- name: Huiying Shen
  orcid: 0000-1111-2222-3333
  inst: 1
ressources: res/
templates: res/templates/
bibliography: res/refs.bib
---

@@

knitr::include_graphics("res/img/fig1a.jpg")
knitr::include_graphics("res/img/fig1b.jpg")
```

@@

\begin{figure}
\includegraphics[width=5.5cm, keepaspectratio,]{res/img/fig2a.jpg}
\includegraphics[width=6.5cm, keepaspectratio,]{res/img/fig2b.jpg}
\caption{(left) Plot of time (x axis) to find target hotspot location for G (‘o’ symbol) vs. NG  (‘x’ symbol) conditions, with time-out declared after 120 sec. of unsuccessful search. Results are shown for each participant (indicated on the y axis and also using color) and at all 10 target locations. (right) Histogram plot showing the distribution of NG time minus G time. The plot aggregates time differences for all participants over all locations; positive times mean the search was faster with G than with NG.}
\label{fig:res}
\end{figure}

>>>>

---
title: "An Audio-Based 3D Spatial Guidance AR System for Blind Users"
titlerunning: Audio-Based 3D Spatial Guidance
authorrunning: J. Couhlan et al.
thanks: Merci !
output:
  pdf_document:
    template: templates/template.tex
    toc: no
    keep_tex: yes
  word_document:
    reference_docx: templates/template.docx
    toc: no
institutes:
- id: 1
  name: The Smith-Kettlewell Eye Research Institute, San Francisco, CA
  emails: coughlan@ski.org, brandon.biggs@ski.org, hshen@ski.org
- id: 2
  name: LITIS, University of Rouen, Normandy, France
  emails: marc-aurele.riviere@univ-rouen.fr
keywords:
- Assisitive Devices
- Augmented Reality
- Auditory Substitution
- Visual Impairment
abstract: Augmented reality (AR) has great potential for blind users because it enables
  a range of applications that provide audio information about specific locations
  or directions in the user’s environment. For instance, the CamIO (“Camera Input-Output”)
  AR app makes physical objects (such as documents, maps, devices and 3D models) accessible
  to blind and visually impaired persons by providing real-time audio feedback in
  response to the location on an object that the user is touching (using an inexpensive
  stylus). An important feature needed by blind users of AR apps such as CamIO is
  a 3D spatial guidance feature that provides real-time audio feedback to help the
  user find a desired location on an object. We have devised a simple audio interface
  to provide verbal guidance towards a target of interest in 3D. The experiment we
  report with blind participants using this guidance interface demonstrates the feasibility
  of the approach and its benefit for helping users find locations of interest.
authors:
- name: James Coughlan
  orcid: 0000-0003-2775-4083
  inst: 1
- name: Brandon Biggs
  inst: 1
- name: Marc-Aurèle Rivière
  orcid: 0000-0002-5108-3382
  inst: 2
- name: Huiying Shen
  inst: 1
templates: templates/
bibliography: refs.bib
---

@@

knitr::include_graphics("img/fig1a.jpg")
knitr::include_graphics("img/fig1b.jpg")
```

@@

\begin{figure}
\includegraphics[width=5.5cm, keepaspectratio,]{img/fig2a.jpg}
\includegraphics[width=6.5cm, keepaspectratio,]{img/fig2b.jpg}
\caption{(left) Plot of time (x axis) to find target hotspot location for G (‘o’ symbol) vs. NG  (‘x’ symbol) conditions, with time-out declared after 120 sec. of unsuccessful search. Results are shown for each participant (indicated on the y axis and also using color) and at all 10 target locations. (right) Histogram plot showing the distribution of NG time minus G time. The plot aggregates time differences for all participants over all locations; positive times mean the search was faster with G than with NG.}
\label{fig:res}
\end{figure}
